A Hedonic Price Analysis of Traffic Noise in the Twin Cities Housing Market

### 2013-09-12 reports/Draft.Rnw
updated correlation matrix code and in paper

\documentclass{article}
\usepackage[round]{natbib}
\usepackage{caption, amsmath, graphicx, setspace, multirow, color, hyperref}

@@

\begin{table}
\caption{Matrix of Pearson Correlation Coefficients for Quantitative Variables}\label{tab:cor}
\includegraphics[width = \textwidth]{../graphs/CorrelationMatrix}
\end{table}

>>>>

\documentclass{article}
\usepackage[round]{natbib}
\usepackage{caption, amsmath, graphicx, setspace, multirow, color, hyperref, array}

\newcolumntype{x}[1]{%
>{\centering\hspace{0pt}}p{#1}}%

@@

\begin{table}
\caption{Matrix of Pearson Correlation Coefficients for Quantitative Variables}\label{tab:cor}
%\includegraphics[width = \textwidth]{../graphs/CorrelationMatrix}
\begin{center}
\small
\tabcolsep=0.05cm
\begin{tabular}{lrrrrrrrrrrr}
  \hline
 & \multicolumn{1}{x{.35in}}{Price} & \multicolumn{1}{x{.38in}}{House} & \multicolumn{1}{x{.35in}}{Lot} & 
 \multicolumn{1}{x{.35in}}{Built} & \multicolumn{1}{x{.35in}}{Noise} & \multicolumn{1}{x{.35in}}{Inc.} & 
 \multicolumn{1}{x{.35in}}{Test} & \multicolumn{1}{x{.35in}}{CBD} & \multicolumn{1}{x{.35in}}{Park} & \multicolumn{1}{x{.35in}}{Lake} & \multicolumn{1}{x{.35in}}{Shop} \tabularnewline 
  \hline
ln Sale Price & 1 &  &  &  &  &  &  &  &  &  &  \tabularnewline 
  House Size & 0.74 & 1 &  &  &  &  &  &  &  &  &  \tabularnewline 
  Lot Size & 0.40 & 0.45 & 1 &  &  &  &  &  &  &  &  \tabularnewline 
  Year Built & 0.49 & 0.52 & 0.47 & 1 &  &  &  &  &  &  &  \tabularnewline 
  Noise & -0.12 & -0.07 & 0.00 & -0.19 & 1 &  &  &  &  &  &  \tabularnewline 
  Income & 0.55 & 0.50 & 0.41 & 0.57 & -0.18 & 1 &  &  &  &  &  \tabularnewline
  Elem. Test Scores & 0.33 & 0.28 & 0.29 & 0.34 & -0.04 & 0.44 & 1 &  &  &  &  \tabularnewline 
  Distance to CBD & 0.35 & 0.45 & 0.43 & 0.58 & -0.04 & 0.53 & 0.35 & 1 &  &  &  \tabularnewline
  Distance to Park & 0.27 & 0.28 & 0.22 & 0.42 & -0.13 & 0.38 & 0.22 & 0.57 & 1 &  &  \tabularnewline
  Distance to Lake & -0.05 & -0.10 & -0.25 & -0.17 & -0.03 & -0.12 & -0.10 & -0.09 & 0.20 & 1 &  \tabularnewline
  Distance to Shop & 0.28 & 0.27 & 0.15 & 0.37 & -0.19 & 0.36 & 0.18 & 0.46 & 0.38 & 0.15 & 1 \tabularnewline
   \hline
\end{tabular}
\end{center} 
\end{table}
